Relationships between environmental variabels and species richness

### 2015-02-10 Doc/ms.Rmd
update with examples about table cross-ref

>>>>

Here is the second paragraph of the introduction.

# Methods

Here is the method section. You can include equations easily. For inline equations, use $\text{var}(X) = p(1-p)$. For display equation, use

\begin{equation}
\text{var}(X) = p(1-p)
\end{equation}

## Results

#### Insert tables by `kable` in knitr package in R

```{r table,results='asis',echo=FALSE,message=F,warning=F}
# load("../R/.RData")
source("../R/rcode.R")
library(knitr)
kable(sprich)
```

Put results inline, e.g. the mean species richness is `r meansprich`.

#### Insert tables by `xtable` package in R

Show as Table. \ref{t:anova}:

```{r echo=F,results='asis',warning=F,message=F}
library(xtable)
envi.summ = xtable(summary(envi.aov),label = "t:anova", caption = "Caption here")
print(envi.summ,
		caption.placement = "top",
	  floating=T,
	  hline.after=NULL,
	  comment = FALSE,
	  add.to.row=list(pos=list(-1,0, nrow(envi.summ)),
	  command=c(
		   '\\toprule\n',
		  '\\midrule\n',
		   '\\bottomrule\n')))
```

#### Insert tables by hand

Show as Table. \ref{t:byhand}:

Table: Caption here. \label{t:byhand}

Col A             Col B       Col C                   Col D
------------      -------     ------------------      ------------------
row 1             190         $112 \pm 2$             $233 \pm 3$
$\eta$            0.13        0.12                    0.12
$\eta^2$          0.14        0.13                    0.50
$\eta^3$          0.15        0.31                    0.52

#### Figures

How about figures? We illustrate this in Fig. \ref{f:plot}.

[f:plot]: Figs/plot.pdf
![Caption here.\label{f:plot}][f:plot]

# References
